\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2013-11-03 doc/paper.tex
Added additional subsection.
added download location, Quick start and requirements (just c+p from manual).

\section{Download and compilation}
\subsection{Quickstart}

\section{Stucture of the spectrum generator}
\subsection{boundary conditions}
Different types, how we match to low energy data.  reference EWSB or merge that section here.
\subsection{RGEs}
\subsection{tree level spectrum}
\subsection{Electroweak symmetry breaking}
\subsection{pole masses}
\subsection{two scale fixed point iteration}
\subsection{Lattice method}
If ready.
\section{Implementing new models}
\section{Adapting the code at the C++ level}
\appendix
\section{Examples}
\section{Tests}

>>>>

\section{Download and compilation}
Flexible SUSY can be downloaded from \url{http://flexiblesusy.hepforge.org}.  
To use FlexibleSUSY please make sure you have the following installed.  
\begin{itemize}
\item Mathematica, version 7 or higher
\item SARAH, version 4.0.0 or higher \url{http://sarah.hepforge.org}
\item C++11 compatible compiler (g++ 4.6.0 or higher, clang++ 3.1 or
  higher)
\item Fortran compiler (gfortran, ifort etc.)
\item Eigen library, version 3.1 \url{http://eigen.tuxfamily.org}
\item Boost library, version 1.36.0 or higher
  \url{http://www.boost.org}
\item GNU scientific library \url{http://www.gnu.org/software/gsl/}
\item lapack (needed for the Lattice algorithm only)
  \url{http://www.netlib.org/lapack/}
\end{itemize}
%
Optional:
%
\begin{itemize}
\item Looptools, version 2.8 or higher
  \url{http://www.feynarts.de/looptools/}
\end{itemize}

\subsection{Quick Start}
Create a MSSM spectrum generator
  \begin{lstlisting}[language=bash]
$ ./createmodel --models=MSSM
$ ./configure --with-models=MSSM
$ make
  \end{lstlisting}
Run the spectrum generator using the default parameter point
  \begin{lstlisting}[language=bash]
$ ./models/MSSM/run_MSSM.x
  \end{lstlisting}
Run the spectrum generator using a SLHA input file
  \begin{lstlisting}[language=bash]
$ ./models/MSSM/run_MSSM.x --slha-input-file=templates/MSSM/LesHouches.in.MSSM --slha-output-file=LesHouches.out.MSSM
  \end{lstlisting}

\section{Stucture of the spectrum generator}
\subsection{boundary conditions}
Different types, how we match to low energy data.  reference EWSB or merge that section here.
\subsection{RGEs}
\subsection{tree level spectrum}
\subsection{Electroweak symmetry breaking}
\subsection{pole masses}
\subsection{two scale fixed point iteration}
\subsection{Lattice method}
If ready.
\subsection{multiple effective models at different scales}
\section{Implementing new models}
\section{Adapting the code at the C++ level}
\appendix
\section{Examples}
\section{Tests}
